A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}

### 2020-01-29 0_reviewer_response.tex

\stepcounter{question}
\subQue{
The authors should highlight their contributions compared to the existing approaches for generating toolpaths with adaptive width.
}\label{contributions}
\Ans{
The contributions were already listed at the end of the introduction, but now we highlight them in comparison to existing techniques.
The focus on the comparison to existing techniques has also been applied to the conclusion.
See also our response to question~\ref{difference_to_jin}.
}
\commits{
66d006d91d406c0064ee1f4f1e4df85fc0821994 % new contributions enumeration
e806d40e5e6d2bbe450c6792b802f0fcce4df645 % lil typo
86c5aa8fab91e326e658f79a0746462fb99ea2b0 % changes to conclusion
}
\paper{1. Introduction}
{
Our contributions are as follows:
\begin{itemize}
\item A geometric framework \revise{for generating densely filling contour-parallel toolpaths employing adaptive width, according to any beading scheme which decides on the bead spacing and widths.}{allowing various adaptive bead width control schemes used to generate contour-parallel toolpaths which minimize under- and overfill.}
\item A specific beading scheme\revise{ for FDM printing}{,} which
reduces the \revise{amount of deviation}{variation} in the extrusion widths \revise{compared to existing literature, }{to within $[0.75w,1.5w]$.}
\revise{and which promotes smooth toolpaths that are equal to the preferred width toward the outline of the shape.}{}
\revise{}{
\item A back pressure compensation approach to accurately realize adaptive bead width on Bowden style hardware systems.
}
\end{itemize}
}
\paper{7. Conclusion}{
In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize underfill and overfill areas.
\revise{}{%af
We introduced beading schemes which improve on the state of the art,
and we have introduced a back pressure compensation method for accurate fabrication of adaptive width.
}

### 2020-01-29 12_conclusions_future_work.tex
lil breakup of long sentence

\section{Conclusion}
In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize underfill and overfill areas\revise{.}{,
we introduced beading schemes which improve on the state of the art
and we have introduced a back pressure compensation method for accurate fabrication of adaptive width.
}

>>>>

\section{Conclusion}
In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize underfill and overfill areas.
\revise{}{%af
We introduced beading schemes which improve on the state of the art,
and we have introduced a back pressure compensation method for accurate fabrication of adaptive width.
}
